---
title: "CITS4009 project 1"
author: "Haitian Wang (23815631)"
student Number: "23815631"
date: "2023-09-03"
output: html_document
---

Welcome to our 'YouTube Data Analysis' Shiny App demonstration. You can view the full video at the following link: https://youtu.be/C16coChaYr0.

# 1. Introduction:
The dataset at hand, titled "Global YouTube Statistics 2023," originates from Kaggle, a renowned platform for data science projects and competitions. The data was meticulously collected by Nidula Elgiriyewithana. For those unfamiliar, Kaggle serves as a hub where data enthusiasts and professionals alike can share datasets, participate in challenges, and contribute to a wealth of shared knowledge in the field of data science.

The "Global YouTube Statistics 2023" dataset provides a comprehensive overview of various YouTube channels, shedding light on key metrics such as the number of subscribers, video views, earnings, and more. With information spanning categories, countries, and other diverse facets, the dataset serves as a significant tool to understand the dynamics of YouTube content creation, viewership patterns, and the emerging trends in digital content consumption. Moreover, with details on the country, it allows for cross-cultural comparisons and insights into regional content preferences.

# 2. Data loading, Overview and Set up

This section lays the foundational steps for any subsequent data analysis operations. Before we can derive any meaningful insights from the data, we need to perform a series of initial processes. These processes not only involve loading the data into our working environment but also familiarizing ourselves with its structure, content, and peculiarities. This foundational knowledge allows us to effectively maneuver through the data, understand its intricacies, and set up the stage for more advanced analyses

## 2.1 Load libraries
```{r Load libraries, message=FALSE}
library(tidyverse) 
library(lubridate)
library(gridExtra)
library(reshape2)
library(grid)
library(shiny)
library(shinyWidgets)
```

## 2.2 Main Data Loading
```{r}
data.path <- './Global_YouTube_Statistics.csv'
youtube_data <- read.csv(data.path)
```

## 2.3 Plotting Theme setting
```{r}
custom_youtube_theme <- function() {
  theme_minimal(base_size = 12) + 
    theme(
      plot.title = element_text(color = "#3366CC", face = "bold", size = 16),
      axis.title = element_text(color = "#666666"),
      axis.text = element_text(color = "#333333"),
      panel.grid.major = element_line(color = "#DDDDDD"),
      panel.grid.minor = element_blank(),
      strip.text.x = element_text(size = 12, colour = "#444444", face = "italic"),
      plot.margin = margin(20, 40, 20, 40)
    )
}
```

## 2.4 Analyze the data structure
```{r}
str(youtube_data)
```
The dataset is a data frame containing 995 observations and 28 variables.
The variables contain different types of data: integers (int), character strings (chr), and numeric values (num).
Several columns like "Youtuber", "category", "Title", "Country", "Abbreviation", "channel_type", and "created_month" are character strings which might be more appropriately treated as factors depending on the analysis. R treats string data as character by default, but they can be converted to factors if they have categories.
Columns such as "rank", "subscribers", "uploads", and others are numerical (either integer or numeric).

## 2.5 Analyze the data Summary 
```{r}
summary(youtube_data)
```

## 2.6 Analyze the first few rows of dataset
```{r}
head(youtube_data)
```

# 3. Data clean and Initial transformations

Data seldom comes in a perfect and ready-to-use format. In fact, raw data usually has inconsistencies, missing values, outliers, and other anomalies that can lead to misinterpretation or inaccurate analysis. The objective of this section is to refine the raw dataset by eliminating these irregularities, ensuring that the data aligns with standard structures and norms. In addition, some transformations help to make the data more suitable and informative for downstream analyses.

## 3.1 Convert string columns
```{r}
youtube_data$Youtuber <- as.character(youtube_data$Youtuber)
youtube_data$Title <- as.character(youtube_data$Title)
```

## 3.2 Convert factor columns
```{r}
youtube_data$Country <- as.factor(youtube_data$Country)
youtube_data$channel_type <- as.factor(youtube_data$channel_type)
```

## 3.3 Identify numeric and non-numeric columns
```{r}
numeric_columns <- names(youtube_data)[sapply(youtube_data, is.numeric)]

non_numeric_columns <- names(youtube_data)[!sapply(youtube_data, is.numeric)]

non_numeric_columns <- setdiff(non_numeric_columns, c("Youtuber", "Title"))
```

## 3.4 # Replace infinite values in numeric columns with their median
```{r}
for (column_name in numeric_columns) {
  
  median_value <- median(youtube_data[[column_name]][is.finite(youtube_data[[column_name]])], na.rm = TRUE)
  
  youtube_data[[column_name]][!is.finite(youtube_data[[column_name]])] <- median_value
}
```

## 3.5 Convert month names to numbers and Create combined date column
```{r}
month_lookup <- c(Jan=1, Feb=2, Mar=3, Apr=4, May=5, Jun=6, Jul=7, Aug=8, Sep=9, Oct=10, Nov=11, Dec=12)

youtube_data$created_month_num <- as.integer(month_lookup[youtube_data$created_month])

youtube_data$combined_created_date <- with(youtube_data, 
                                           ifelse(!is.na(created_year) & !is.na(created_month_num) & !is.na(created_date),
                                                  as.Date(paste(created_year, created_month_num, created_date, sep="-"), format="%Y-%m-%d"), 
                                                  NA))
```

## 3.6. Replace na or other values with NA
```{r}
youtube_data[youtube_data == "nan"] <- NA
youtube_data[youtube_data == "NaN"] <- NA
```



## 3.7 Replace 0 views and uploads with their respective means
```{r}
youtube_data$video.views[youtube_data$video.views == 0] <- mean(youtube_data$video.views[youtube_data$video.views > 0], na.rm = TRUE)
youtube_data$uploads[youtube_data$uploads == 0] <- mean(youtube_data$uploads[youtube_data$uploads > 0], na.rm = TRUE)
```


## 3.8 Clean negative values in highest_monthly_earnings column
```{r}
min_positive_earning <- min(youtube_data$highest_monthly_earnings[youtube_data$highest_monthly_earnings > 0], na.rm = TRUE)
youtube_data$highest_monthly_earnings[youtube_data$highest_monthly_earnings <= 0] <- min_positive_earning
```


## 3.9 Replace NA values in numeric columns with median
```{r}
for (column_name in numeric_columns) {
  
  median_value <- median(youtube_data[[column_name]], na.rm = TRUE)
  
  youtube_data[[column_name]][is.na(youtube_data[[column_name]])] <- median_value
  
}
```


## 3.10 Check missing data count
```{r}
na_counts <- apply(is.na(youtube_data), 2, sum)
print(na_counts)
```

## 3.11 Determine median views for segmentation
```{r}
median_views <- median(youtube_data$video_views, na.rm = TRUE)
```

## 3.12 Segment the data based on median views
```{r}
high_views <- youtube_data[youtube_data$video_views > median_views, ]
low_views <- youtube_data[youtube_data$video_views <= median_views & !is.na(youtube_data$video_views), ]
```

## 3.12 Analyze missing data in each segment
```{r}
na_high_views <- apply(is.na(high_views), 2, sum)
na_low_views <- apply(is.na(low_views), 2, sum)
```

# 4. Data Analyzing and Ploting

This section aims to shed light on the relationships between various attributes present in the YouTube dataset. The purpose is to discern patterns, anomalies, and correlations that might lead to actionable insights for content creators and other stakeholders.
## 4.1 Analyzing Relationship between Subscribers and Video.views
```{r}
p1 <- ggplot(data = youtube_data, mapping = aes(x = subscribers)) +
  geom_histogram(aes(y = after_stat(density)), bins = 50, fill = "#99CCFF", color = "#3366CC") +
  geom_density(color = "#3366CC") +
  scale_x_continuous(trans = 'log10') +
  ggtitle("YouTube Subscribers (Log Scale)") +
  custom_youtube_theme()
print(p1)

p2 <- ggplot(data = youtube_data, mapping = aes(x = subscribers)) +
  geom_histogram(aes(y = after_stat(density)), bins = 100, fill = "#99CCFF", color = "#3366CC") +
  geom_density(color = "#3366CC") +
  coord_cartesian(xlim = c(12300000, 50000000)) +
  ggtitle("YouTube Subscribers (12.3M to 50M)")

p3 <- ggplot(data = youtube_data, mapping = aes(x = video.views)) +
  geom_histogram(aes(y = after_stat(density)), bins = 50, fill = "#99CCFF", color = "#3366CC") +
  geom_density(color = "#3366CC") +
  scale_x_continuous(trans = 'log10', labels = scales::comma) +
  ggtitle("YouTube Video Views (Log Scale)") +
  custom_youtube_theme()
print(p3)

p4 <- ggplot(data = youtube_data, mapping = aes(x = video.views)) +
  geom_histogram(aes(y = after_stat(density)), bins = 100, fill = "#99CCFF", color = "#3366CC") +
  geom_density(color = "#3366CC") +
  coord_cartesian(xlim = c(4.288e+09, 1.355e+10)) +
  ggtitle("YouTube Video Views (4.288B to 13.55B)") +
  custom_youtube_theme()
print(p4)
 
 
p5 <- ggplot(youtube_data, aes(x=subscribers, y=video.views)) +
  geom_point(aes(color=channel_type), alpha=0.5) +
  geom_smooth(method=lm) +
  labs(title="Relation between Subscribers and Video Views",
       x="Subscribers", y="Video Views", color="Channel Type") +
  custom_youtube_theme()
print(p5)
```


```{r}
cor.test(youtube_data$subscribers, youtube_data$video.views, method="pearson")
```
On the YouTube platform, there's a significant positive correlation between the number of subscribers and video views, with a Pearson correlation coefficient of 0.7699. This suggests that as a channel's subscriber count rises, there's a high likelihood that its video views will also increase. Moreover, from the scatter plot, it appears that this relationship is consistent across different types of channels, indicated by varying colors. When smoothed with a linear model, we observe a linear increase in the predicted video views as the subscriber count goes up.
However, there are also some 'outliers', channels with relatively high subscriber counts but fewer video views, or vice versa. This discrepancy might be due to certain channels having one or two viral videos that garner a significant number of views, but without a corresponding increase in the channel's overall subscribers.


## 4.2 Analyzing Relationship between Subscribers and Country
```{r}
top_countries <- youtube_data %>%
  count(Country) %>%
  arrange(-n) %>%
  head(10)

filtered_data <- youtube_data %>%
  filter(Country %in% top_countries$Country)

p7 <- ggplot(data = filtered_data, mapping = aes(x = Country)) +
  geom_bar(fill = "#99CCFF", color = "#3366CC") +
  ggtitle("Number of YouTubers in Top 10 Countries") +
  coord_flip()+
  custom_youtube_theme()
print(p7)


gd <- filtered_data %>%
  group_by(Country) %>%
  summarise(average_subscribers = mean(subscribers, na.rm = T))

p8 <- ggplot(data = filtered_data,
             mapping = aes(y = subscribers, x = Country))+
  geom_violin(fill ='lightgray')+
  geom_point(data = gd, aes(y = average_subscribers, shape='mean'), color='darkred', size=4)+
  ggtitle("Distribution of Subscribers in Top 10 Countries") +
  coord_flip()+
  custom_youtube_theme()
print(p8)
```
From the "Number of YouTubers per Country" chart, it's evident that there's a significant variance in the number of YouTubers across countries. Some countries have a notably higher count of YouTubers than others.

The "Average Subscribers per Country" chart, on the other hand, depicts the average subscriber count for YouTubers in various countries. This reveals which countries' YouTubers, on average, have more subscribers. Such differences could be attributed to YouTubers from these nations being more popular or due to a higher usage rate of YouTube in that particular country.


## 4.3 Analyzing Relationship between Earning and video.views
```{r}
p9 <- ggplot(data = youtube_data, mapping = aes(x = highest_monthly_earnings)) +
  geom_histogram(aes(y = after_stat(density)), bins = 50, fill = "#99CCFF", color = "#3366CC") +
  geom_density(color = "#3366CC") +
  scale_x_continuous(trans = 'log10', labels = scales::comma) +
  ggtitle("Histogram of Highest Monthly Earnings (Log Scale)") +
  custom_youtube_theme()
print(p9)

p10 <- ggplot(data = youtube_data, mapping = aes(y = highest_monthly_earnings)) +
  geom_boxplot(fill = "#99CCFF", color = "#3366CC") +
  ggtitle("Boxplot of Highest Monthly Earnings") +
  custom_youtube_theme()
print(p10)

p11 <- ggplot(youtube_data, aes(x=video.views, y=highest_monthly_earnings)) +
  geom_point(aes(color=channel_type), alpha=0.5) +
  geom_smooth(method=lm) + # 添加线性回归线
  labs(title="Relation between Video Views and Highest Monthly Earnings",
       x="Video Views", y="Highest Monthly Earnings", color="Channel Type") +
  custom_youtube_theme()
print(p11)

cor_result <- cor.test(youtube_data$video.views, youtube_data$highest_monthly_earnings, method="pearson")
```
"Pearson Correlation Coefficient Value: The 'cor' value is 0.5495619, indicating a moderate positive linear relationship between video.views and highest_monthly_earnings. This means that as video views increase, the highest monthly earnings of a YouTuber tend to increase as well.
Significance Level: The p-value is less than 2.2e-16. This is an extremely small p-value, far below typical significance levels (like 0.05). This suggests that the association we observe in the data is statistically significant and is unlikely to have occurred by random chance.
Based on the above analysis, we can conclude that, within the provided YouTube data, there's a significant moderate positive linear relationship between video views and a YouTuber's highest monthly earnings. This might suggest that more video views could lead to higher monthly earnings


## 4.4 Analyzing Relationship between created_year and Subscribers
```{r}
p12 <- ggplot(data = youtube_data, mapping = aes(x = created_year)) +
  geom_histogram(aes(y = after_stat(density)), binwidth=1, fill = "#99CCFF", color = "#3366CC") +
  geom_density(color = "#3366CC") +
  ggtitle("Distribution of YouTube Channel Creation Year (Density)") +
  custom_youtube_theme()
print(p12)

p13 <- ggplot(data = youtube_data, mapping = aes(x = created_year)) +
  geom_histogram(aes(y = after_stat(density)), binwidth=0.5, fill = "#99CCFF", color = "#3366CC") +
  geom_density(color = "#3366CC") +
  coord_cartesian(xlim = c(2010, 2020)) +
  ggtitle("YouTube Channel Creation Year (2010 to 2020)") +
  custom_youtube_theme()
print(p13)

youtube_data_filtered <- youtube_data[youtube_data$created_year >= 2010 & youtube_data$created_year <= 2020,]

p14 <- ggplot(data = youtube_data_filtered, aes(x = factor(created_year), y = subscribers)) +
  geom_bar(stat = "summary", fun = mean, fill = "#99CCFF", color = "#3366CC", width = 0.7) +
  geom_smooth(aes(group = 1), method = "lm", color = "red", se = FALSE) +
  labs(title = "Relation between Year of Creation and Average Subscribers (2010-2020)",
       x = "Year of Creation", y = "Average Subscribers") +
  custom_youtube_theme()
print(p14)

cor_result <- cor.test(youtube_data_filtered$created_year, youtube_data_filtered$subscribers, method = "pearson")
```
On the YouTube platform, we further explored the relationship between the year a channel was created and its subscriber count. From the Pearson correlation coefficient analysis, it's evident that there's a negative correlation between the channel's creation year and the number of subscribers, with a correlation coefficient of -0.1419. Although this relationship is relatively weak, it's statistically significant as the p-value is well below 0.05.

This might suggest that channels created earlier tend to have fewer subscribers compared to those established more recently. This could be attributed to various factors such as the evolution and development of the YouTube platform, market saturation, refreshing content ideas, and shifts in audience preferences.

By plotting a scatter graph, we can visually see the relationship between the channel's creation year and its subscriber count. The red linear model shows this trend. While this model simplifies the intricate real-world relationship, it provides a preliminary perspective.

It's worth noting that from our previous analysis, we determined that there's a significant positive correlation between subscriber count and video views. Now, recognizing a negative correlation between the channel's creation year and subscriber count implies that newer channels might need to exert more effort to attract viewers and increase video views.


# 5. Shiny APP
In this section, we'll provide an interactive application using R's Shiny framework to visually explore the YouTube data.

```{r}
ui <- fluidPage(
  titlePanel("YouTube Data Analysis"),
  sidebarLayout(
    
    
    sidebarPanel(
      selectInput("plot_type", "Select plot type:", choices = c("Scatter", "Pairwise", "Barplot")),
      conditionalPanel(
        condition = "input.plot_type == 'Pairwise'",
        pickerInput(
          inputId = "selected_attributes_numeric",
          label = "Select numeric attributes:",
          choices = numeric_columns,
          multiple = TRUE,
          options = list(`actions-box` = TRUE)
        )
      ),
      conditionalPanel(
        condition = "input.plot_type == 'Scatter'",
        selectInput("x_attr", "Select x-axis attribute:", numeric_columns),
        selectInput("y_attr", "Select y-axis attribute:", numeric_columns)
      ),
      conditionalPanel(
        condition = "input.plot_type == 'Barplot'",
        pickerInput(
          inputId = "selected_attributes_non_numeric",
          label = "Select non-numeric attributes:",
          choices = non_numeric_columns,
          multiple = FALSE
        )
      )
    ),
    
    
    mainPanel(
      textOutput("select_prompt"),
      plotOutput("plot", height = "400px", width = "800px")
    )
  )
)

# Server部分
server <- function(input, output) {
  
  output$plot <- renderPlot({
    if (input$plot_type == "Pairwise") {
      if (length(input$selected_attributes_numeric) < 2) {
        return()
      }
      selected_data <- youtube_data[, input$selected_attributes_numeric, drop=FALSE]
      pairs(selected_data)
    } 
    else if (input$plot_type == "Barplot" && !is.null(input$selected_attributes_non_numeric)) {
      selected_column <- input$selected_attributes_non_numeric
      selected_data <- table(youtube_data[[selected_column]])
      barplot(selected_data, main=paste("Barplot of", selected_column), las=2)
    }
    else if (input$plot_type == "Scatter") {
      x_attr <- input$x_attr
      y_attr <- input$y_attr
      plot(youtube_data[[x_attr]], youtube_data[[y_attr]],
           xlab = x_attr, ylab = y_attr, main = paste("Scatter plot of", x_attr, "vs", y_attr))
      abline(lm(youtube_data[[y_attr]] ~ youtube_data[[x_attr]]), col = "blue")  # Linear regression line
    }
  })
  
}

shinyApp(ui = ui, server = server)
```





